### 2021-04-13 assertions/doc/thesis-bernhardt/chapters/1-introduction.tex
Revision Chapter 2

\section{Structure overview}
The structure of this thesis is as follows: in the first instance, \chapref{chap:use_cases} defines a set of logical formulas that describe parameter properties and are suitable for distributed assertion checking. Given this set, it demonstrates various practical use-cases for such properties and formalizes the costs of checking them locally, s.t. they can later be referenced to assess the efficiency of the distributed approach. \chapref{chap:offline} describes the generic aspects of the off-chain design and infrastructure, i.a. the definition of a syntax to express assertions on top of the logical formulas and how they are transformed to code that checks for counterexamples. Additionally, it analyses the effectiveness of the statistical validation for a given input and provides a formula to compute the lower bound of validators necessary to obtain a reliable result. Subsequently, \chapref{chap:offline_tezos} gives a brief introduction to Tezos, before it covers target specific aspects of the off-chain design. Besides identifying necessary extensions to Michelson's instruction set and virtual machine, it explores various orchestration strategies between assertion and contract code. The chapter closes with a cost analysis of distributed assertion checking on Tezos with the chosen orchestration strategy. In conclusion, the last chapter recaps the achieved results, 
addresses any open questions or issues and provides an outlook on upcoming work on this topic.

>>>>

\section{Structure overview}
The structure of this thesis is as follows: in the first instance, \chapref{chap:use_cases} defines a set of logical formulas suitable for distributed assertion checking. Given this set, it demonstrates various practical use-cases for such properties and formalizes the costs of checking them locally, s.t. they can later be referenced to assess the efficiency of the distributed approach. \chapref{chap:offline} describes the generic aspects of the off-chain design and infrastructure, i.a. the definition of a syntax to express assertions on top of the logical formulas and how they are transformed to code that checks for counterexamples. Additionally, it analyses the effectiveness of the statistical validation for a given input and provides a formula to compute the lower bound of validators necessary to obtain a reliable result. Subsequently, \chapref{chap:offline_tezos} gives a brief introduction to Tezos, before it covers target specific aspects of the off-chain design. Besides identifying necessary extensions to Michelson's instruction set and virtual machine, it explores various orchestration strategies between assertion and contract code. The chapter closes with a cost analysis of distributed assertion checking on Tezos with the chosen orchestration strategy. In conclusion, the last chapter recaps the achieved results, 
addresses open questions or issues and provides an outlook on upcoming work on this topic.
